A 3D curvilinear skeletonization algorithm with application to path tracing

### 2012-11-29 skeleton_and_pathtracing.tex
Autres corrections reviewer 1, a John de jouer maintenant

In the following, we introduce a new method in the cubical complex framework, requiring no user input, for obtaining a curvilinear skeleton yielding satisfactory geometrical properties. Our method is based on the two previously listed strategies: its finds, during thinning, elements whose neighbourhood configuration is interesting, and uses a function on these elements to decide to preserve them, or not, in the result.

@@

The \myem{maximal $1$-ball of $S$ centered on $x$} is the set $\MaxOneBall{S}(x)=\{y \in \Zset^n | \dist1(x,y) < \Dist1{S}(x)\}$.
We set, for all $x \in S$, the map $\DD1{S}: \Zset^n \rightarrow \Nset$ such that $\DD1{S}(x) = \displaystyle \max_{x \in \MaxOneBall{S}(y)} \Dist1{S}(y)$: this value indicates the radius of the largest maximal $1$-ball contained in $S$ and containing $x$. If $x \in \Compl{S}$, we set $\DD1{S}(x) = 0$. The map $\DD1{S}$ is known as the opening function of $S$ based on the $1$-distance (also called the granulometry function) \cite{Matheron67}: it allows to compute efficiently results of morphological openings by balls of various radius, and gives information on the local thickness of an object.

>>>>

In the following, we introduce a new method in the cubical complex framework, requiring no user input, for obtaining a curvilinear skeleton yielding satisfactory geometrical properties. Our method is based on the two previously listed strategies: it finds, during thinning, elements whose neighbourhood configuration is interesting, and uses a function on these elements to decide whether to preserve them, or not, in the result.

@@

The \myem{maximal $1$-ball of $S$ centered on $x$} is the set $\MaxOneBall{S}(x)=\{y \in \Zset^n | \dist1(x,y) < \Dist1{S}(x)\}$.
We set, for all $x \in S$, the map $\DD1{S}: \Zset^n \rightarrow \Nset$ such that $\DD1{S}(x) = \displaystyle \max_{x \in \MaxOneBall{S}(y)} \Dist1{S}(y)$: this value indicates the radius of a largest maximal $1$-ball contained in $S$ and containing $x$. If $x \in \Compl{S}$, we set $\DD1{S}(x) = 0$. The map $\DD1{S}$ is known as the opening function of $S$ based on the $1$-distance (also called the granulometry function) \cite{Matheron67}: it allows to compute efficiently results of morphological openings by balls of various radius, and gives information on the local thickness of an object.
